---
title: "Practice"
output: html_document
---
  
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
```
```{r}
library(jsonlite)
library(tidyverse)
library(dplyr)
```

```{r}
getwd()
demo_table <- read.csv(file='C:/Users/jeja9/Bootcamp/Week15_R/R_Statistical_Analysis/Practice/Resources/demo.csv',check.names=F,stringsAsFactors = F)
demo_table
```
```{r}
demo_table2 <- fromJSON(txt='C:/Users/jeja9/Bootcamp/Week15_R/R_Statistical_Analysis/Practice/Resources/demo.json')
demo_table2
```


```{r}
demo_table3 <- read.csv(file='C:/Users/jeja9/Bootcamp/Week15_R/R_Statistical_Analysis/Practice/Resources/demo2.csv',check.names=F,stringsAsFactors = F)
head(demo_table3)
```


#subset
```{r}
filter_table2 <- subset(demo_table2, price > 10000 & drive == "4wd" & "clean" %in% title_status) #filter by price and drivetrain
head(filter_table2)
```

```{r}
# using brackets
filter_table3 <- demo_table2[("clean" %in% demo_table2$title_status) & (demo_table2$price > 10000) & (demo_table2$drive == "4wd"),]
head(filter_table3)
```

```{r}
summarize_demo <- demo_table2 %>% group_by(condition) %>%
summarize(Mean_Mileage=mean(odometer), .groups = 'keep') #create summary table
head(summarize_demo)

```

```{r}
summarize_demo <- demo_table2 %>% group_by(condition) %>%
summarize(Mean_Mileage=mean(odometer),Maximum_Price=max(price),Num_Vehicles=n(), .groups = 'keep') #create summary table with multiple columns
head(summarize_demo)
```
#long table
```{r}
long_table <- gather(demo_table3,key="Metric",value="Score",buying_price:popularity)
head(long_table)
```

```{r}
head(mpg)
plt <- ggplot(mpg,aes(x=class)) #import dataset into ggplot2
plt + geom_bar() #plot a bar plot
```

```{r}
mpg_summary <- mpg %>% group_by(manufacturer) %>% summarize(Vehicle_Count=n(), .groups = 'keep') #create summary table
plt <- ggplot(mpg_summary,aes(x=manufacturer,y=Vehicle_Count)) #import dataset into ggplot2
plt + geom_col() #plot a bar plot
```

```{r}
#format of plot
plt + geom_col() + xlab("Manufacturing Company") + ylab("Number of Vehicles in Dataset") + #plot a boxplot with labels
theme(axis.text.x=element_text(angle=45,hjust=1)) #rotate the x-axis label 45 degrees
```

# box plot from mpg data
```{r}
plt <- ggplot(mpg,aes(y=hwy))#import dataset into ggplot2
plt + geom_boxplot() #add boxplot
```

# box plot with category
```{r}
plt <- ggplot(mpg,aes(x=manufacturer,y=hwy)) #import dataset into ggplot2
plt + geom_boxplot() + theme(axis.text.x=element_text(angle=45,hjust=1)) # 
```

# Heatmap of average highway fuel efficiency across the type of vehicle class from 1999 to 2008
```{r}
mpg_summary <- mpg %>% group_by(class,year) %>% summarize(Mean_Hwy=mean(hwy), .groups = 'keep')
plt <- ggplot(mpg_summary, aes(x=class,y=factor(year),fill=Mean_Hwy))
plt + geom_tile() + labs(x="Vehicle Class",y="Vehicle Year",fill="Mean Highway (MPG)")
```
#average highway fuel e􀂨ciency across each vehicle model from 1999 to 2008
```{r}
mpg_summary <- mpg %>% group_by(model,year) %>% summarize(Mean_Hwy=mean(hwy), .groups = 'keep') #create summary table
plt <- ggplot(mpg_summary, aes(x=model,y=factor(year),fill=Mean_Hwy)) #import dataset into ggplot2
plt + geom_tile() + labs(x="Model",y="Vehicle Year",fill="Mean Highway (MPG)") + theme(axis.text.x = element_text(angle=90,hjust=1,vjust=.5)) #rotate x-axis labels 90 degrees
```

# add additional plots to our visualization by adding additional geom functions
```{r}
plt <- ggplot(mpg,aes(x=manufacturer,y=hwy)) #import dataset into ggplot2
plt + geom_boxplot() + #add boxplot
theme(axis.text.x=element_text(angle=45,hjust=1)) + #rotate x-axis labels 45 degrees
geom_point() #overlay scatter plot on top
```

# mapping argument
```{r}
mpg_summary <- mpg %>% group_by(class) %>%
summarize(Mean_Engine=mean(displ), .groups = 'keep') #create summary table
plt <- ggplot(mpg_summary,aes(x=class,y=Mean_Engine)) #import dataset into ggplot2
plt + geom_point(size=4) + labs(x="Vehicle Class",y="Mean Engine Size") #add scatter plot
```
# mean plus standard deviation
```{r}
mpg_summary <- mpg %>% group_by(class) %>%
summarize(Mean_Engine=mean(displ),SD_Engine=sd(displ), .groups = 'keep')
plt <- ggplot(mpg_summary,aes(x=class,y=Mean_Engine)) #import dataset into ggplot2
plt + geom_point(size=4) + labs(x="Vehicle Class",y="Mean Engine Size") + #add scatter plot with labels
geom_errorbar(aes(ymin=Mean_Engine-SD_Engine,ymax=Mean_Engine+SD_Engine)) #overlay with error bars
```
#visualize the different vehicle fuel effciency ratings by manufacturer
```{r}
mpg_long <- mpg %>% gather(key="MPG_Type",value="Rating",c(cty,hwy)) #conve
head(mpg_long)
plt <- ggplot(mpg_long,aes(x=manufacturer,y=Rating,color=MPG_Type)) #import
plt + geom_boxplot() + theme(axis.text.x=element_text(angle=45,hjust=1)) #
```
#visualize the different types of fuel e????ciency within the visualization using the facet_wrap() function.
```{r}
plt <- ggplot(mpg_long,aes(x=manufacturer,y=Rating,color=MPG_Type)) #import dataset into ggplot2
plt + geom_boxplot() + facet_wrap(vars(MPG_Type)) + #create multiple boxplots, one for each MPG type
theme(axis.text.x=element_text(angle=45,hjust=1),legend.position = "none") + xlab("Manufacturer") #rotate xaxis labels
```




# visualize the distribution of driven miles for our entire population dataset
```{r}
population_table <- read.csv(file='Resources/used_car_data.csv',check.names = F,stringsAsFactors = F) #import used car dataset
head(population_table)
plt <- ggplot(population_table,aes(x=log10(Miles_Driven))) #import dataset into ggplot2
plt + geom_density() #visualize distribution using density plot
```
# create a sample dataset using dplyr's sample_n() function.
```{r}
sample_table <- population_table %>% sample_n(50) #randomly sample 50 data points
plt <- ggplot(sample_table,aes(x=log10(Miles_Driven))) #import dataset into ggplot2
plt + geom_density() #visualize distribution using density plot
```


#  One-Sample t-Test
```{r}
#compare sample versus population means
t.test(log10(sample_table$Miles_Driven),mu=mean(log10(population_table$Miles_Driven)))

```



#two-sample t-Test 
```{r}
sample_table <- population_table %>% sample_n(50) #generate 50 randomly sam
sample_table2 <- population_table %>% sample_n(50) #generate another 50 random
t.test(log10(sample_table$Miles_Driven),log10(sample_table2$Miles_Driven))
```
# pair t-test
```{r}
mpg_data <- read.csv(file='Resources/mpg_modified.csv',check.names = F,stringsAsFactors = F) #import used car dataset
mpg_1999 <- mpg_data %>% filter(year==1999) #select only data points where the year is 1999
mpg_2008 <- mpg_data %>% filter(year==2008) #select only data points where the year is 2008
t.test(mpg_1999$hwy,mpg_2008$hwy,paired = T) #compare the mean difference

```


# ANOVA Test
```{r}
# the cyl is considered a numerical interval vector, not a categorical vector. 
# Therefore, we must clean our data before we begin,
mtcars_filt <- mtcars[,c("hp","cyl")] #filter columns from mtcars dataset
mtcars_filt$cyl <- factor(mtcars_filt$cyl) #convert numeric column to factor
aov(hp ~ cyl,data=mtcars_filt) #compare means across multiple levels
summary(aov(hp ~ cyl,data=mtcars_filt))
```

# pair t-test
```{r}
used_cars <- read.csv(file='Resources/used_car_data.csv',check.names = F,stringsAsFactors = F)

cor(used_cars$Miles_Driven,used_cars$Selling_Price) #calculate correlation

```

#produce a correlation matrix for our used_cars dataset
```{r}
used_matrix <- as.matrix(used_cars[,c("Selling_Price","Present_Price","Miles_Driven")])
#convert data frame into numeric matrix
cor(used_matrix)
```

# Linear Regression
```{r}
model <- lm(qsec ~ hp,mtcars) #create linear model
summary(model)
yvals <- model$coefficients['hp']*mtcars$hp + model$coefficients['(Intercept)'] #determine y-axis values from linear model
plt <- ggplot(mtcars,aes(x=hp,y=qsec)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") #plot scatter
```

# Multiple linear Regression
```{r}
lm(qsec ~ mpg + disp + drat + wt + hp,data=mtcars) #generate multiple line
summary(lm(qsec ~ mpg + disp + drat + wt + hp,data=mtcars)) #generate summa
```

# chi-squared test
```{r}
#statistical difference in the distributions of vehicle class across 1999 and 2008 from our mpg
table(mpg$class,mpg$year) #generate contingency table
#pass the contingency table to the chisq.test() function:
tbl <- table(mpg$class,mpg$year) #generate contingency table
chisq.test(tbl) #compare categorical distributions
```
