---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

# Deliverable 1: Linear Regression to Predict MPG
```{r}
MechaCar_mpg <- read.csv(file="Resources/MechaCar_mpg.csv")
head(MechaCar_mpg)
```

# Multiple linear Regression
```{r}

mpg_lm <-lm(mpg ~ vehicle_length + vehicle_weight + spoiler_angle + ground_clearance + AWD + mpg, MechaCar_mpg) 
# summarize linear regression
summary(mpg_lm ) 
```
# Linear Regression for each vaiable


### Function to create the text equation
```{r}
lm_eqn <- function(df, lm_object) {
  eq <-
    substitute(
      italic(y) == a %.%italic(x) + b * ","  ~ italic(r) ^ 2 ~ "=" ~ r2 * ","  ~ italic(p.) ~ "=" ~ p,
      list(
        a = format (summary(lm_object)$coefficients[2,1], digits =3),
        b = format (summary(lm_object)$coefficients[1,1], digits =3),
        r2 = format (summary(lm_object)$r.squared, digits =3),
        p = format (summary(lm_object)$coefficients[2,4], digits =3)
        )
    )
  as.character(as.expression(eq))
}
```


### vehicle_length vs mpg
```{r}
model <- lm(mpg ~ vehicle_length, data=MechaCar_mpg)
summary(model)

```
```{r}
#determine y-axis values from linear model
yvals <- model$coefficients[2]*MechaCar_mpg$vehicle_length + model$coefficients[1]
# get the equation object in a format for use in ggplot2
eqn <- lm_eqn(MechaCar_mpg$vehicle_length, model)

# plot with text
plt <- ggplot(MechaCar_mpg,aes(x=vehicle_length,y=mpg)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") +
annotate("text", x = 14, y = 78, label = eqn, parse = TRUE)
```


### vehicle_weight vs mpg
```{r}
model <- lm(mpg ~ vehicle_weight, data=MechaCar_mpg)
summary(model)
```

```{r}
#determine y-axis values from linear model
yvals <- model$coefficients[2]*MechaCar_mpg$vehicle_weight + model$coefficients[1] 
# get the equation object in a format for use in ggplot2
eqn <- lm_eqn(MechaCar_mpg$vehicle_weight, model)
# plot with text
plt <- ggplot(MechaCar_mpg,aes(x=vehicle_weight,y=mpg)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") +
annotate("text", x = 4000, y = 78, label = eqn, parse = TRUE)
```

### spoiler_angle vs mpg
```{r}
model <- lm(mpg ~ spoiler_angle, data=MechaCar_mpg)
summary(model)
```
```{r}
# get the equation object in a format for use in ggplot2
eqn <- lm_eqn(MechaCar_mpg$spoiler_angle, model)
#determine y-axis values from linear model
yvals <- model$coefficients[2]*MechaCar_mpg$spoiler_angle + model$coefficients[1] 
# plot with text
plt <- ggplot(MechaCar_mpg,aes(x=spoiler_angle,y=mpg)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") +
annotate("text", x = 30, y = 78, label = eqn, parse = TRUE)
```


### ground_clearance vs mpg
```{r}
model <- lm(mpg ~ ground_clearance, data=MechaCar_mpg)
summary(model)

```
```{r}
#determine y-axis values from linear model
yvals <- model$coefficients[2]*MechaCar_mpg$ground_clearance + model$coefficients[1]
# get the equation object in a format for use in ggplot2
eqn <- lm_eqn(MechaCar_mpg$ground_clearance, model)
# plot with text
plt <- ggplot(MechaCar_mpg,aes(x=ground_clearance,y=mpg)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") +
annotate("text", x = 10, y = 78, label = eqn, parse = TRUE)
```


### AWD vs mpg
```{r}
model <- lm(mpg ~ AWD, data=MechaCar_mpg)
summary(model)
```
```{r}
#determine y-axis values from linear model
yvals <- model$coefficients[2]*MechaCar_mpg$AWD + model$coefficients[1]
# get the equation object in a format for use in ggplot2
eqn <- lm_eqn(MechaCar_mpg$AWD, model)
# plot with text
plt <- ggplot(MechaCar_mpg,aes(x=AWD,y=mpg)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") +
annotate("text", x = 0.5, y = 78, label = eqn, parse = TRUE)
```


### mpg vs mpg
```{r}
model <- lm(mpg ~ mpg, data=MechaCar_mpg)
summary(model)

```
```{r}
#determine y-axis values from linear model
yvals <- model$coefficients[2]*MechaCar_mpg$mpg + model$coefficients[1] 
# plot with text
plt <- ggplot(MechaCar_mpg,aes(x=mpg,y=mpg)) #import dataset into ggplot2
plt + geom_point() + geom_line(aes(y=yvals), color = "red") 
```



# Deliverable 2: The suspension coil summary statistics

### 
```{r}
suspension_coil <- read.csv(file="Resources/Suspension_Coil.csv", stringsAsFactors = F)
head(suspension_coil)
```
###  total_summary dataframe
```{r}
Total_summary <- suspension_coil %>%         
                  summarize(Mean=mean(PSI), 
                              Median=median(PSI), 
                              Variance=var(PSI),
                              SD=sd(PSI))
Total_summary
```


### lot_summary dataframe
```{r}
lot_summary <- suspension_coil %>% group_by(Manufacturing_Lot)  %>%            
                 summarize(Mean=mean(PSI), 
                              Median=median(PSI), 
                              Variance=var(PSI),
                              SD=sd(PSI), .groups = 'keep')
lot_summary
```

# Deliverable 3: T-Tests on Suspension Coils

### t-test forall manufacturing lots
```{r}
# t-test that compares all manufacturing lots against mean PSI of the population
# One sample t-test;;
t.test(suspension_coil$PSI, mu=mean(suspension_coil$PSI))

```
### Three t-tests that compare each manufacturing lot against mean PSI of the population
```{r}
table_Lot1 <- subset(suspension_coil, Manufacturing_Lot == "Lot1")
t.test(table_Lot1$PSI, mu=mean(table_Lot1$PSI))#compare the mean difference
table_Lot2 <- subset(suspension_coil, Manufacturing_Lot == "Lot2")
t.test(table_Lot2$PSI, mu=mean(table_Lot2$PSI))#compare the mean difference
table_Lot3 <- subset(suspension_coil, Manufacturing_Lot == "Lot3")
t.test(table_Lot3$PSI, mu=mean(table_Lot3$PSI))#compare the mean difference
```
